%-------------------------
% Resume in LaTeX
% Author : Max Tong (based on Jake Gutierrez template)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Workday/ATS helpers
\newcommand{\daterange}[2]{#1 - #2} 

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \textbf{#1}\hfill #4\\
  \textit{\small #3}\hfill \textit{\small #2}\\
  \vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \textit{\small#1}\hfill \textit{\small #2}\\
  \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \small#1\hfill \textit{#2}\\
  \vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Max Tong} \\ \vspace{1pt}
    \small 864-207-0752 \textbar\ 
    \href{mailto:maxtong2027@u.northwestern.edu}{\underline{maxtong2027@u.northwestern.edu}} \textbar\ 
    \href{https://www.linkedin.com/in/max-tong-1957b0342/}{\underline{linkedin.com/in/max-tong}} \textbar\ 
    \href{https://github.com/maxtong2023}{\underline{github.com/maxtong2023}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northwestern University}{Evanston, IL}
      {Bachelor of Science in Computer Science - Minor in Math - Major GPA: 3.7/4.0}{Expected Jun 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems (C/C++), Artificial Intelligence, Machine Learning, Scalable Software (AWS), Networking (TCP/UDP)}
        \resumeItem{\textbf{Clubs \& Organizations:} Northwestern Garage Residency, Formula SAE, Competitive Programming (ICPC)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AT\&T}{\daterange{Jun 2026}{Present}}
      {Software Engineering Intern}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Engineered a Random Forest and LightGBM fraud detection model achieving \textbf{0.90 AUC} in replicating Visa Decision Manager outputs, enabling \textbf{80\%} reduction in third-party API calls for Cricket BYOD eSIM activations}
        \resumeItem{
        Performed EDA and feature engineering on MongoDB fraud data using Pandas \& deployed model via Databricks
        }
        \resumeItem{
        Implemented a Redis caching Python + FastAPI microservice for fraud velocity and morphing data, screening \textbf{10,000+} daily transactions at sub-250ms p95 latency to flag fraud before impacting customers.
        }
      \resumeItemListEnd

    \resumeSubheading
      {TwoCann}{\daterange{Jun 2024}{Present}}
      {Founder}{Evanston, IL}
      \resumeItemListStart
        \resumeItem{Built, shipped, and scaled a cross-platform consumer app to \textbf{1,000+} registered users on \textbf{Firebase} and \textbf{Google Cloud Platform} as sole developer.}
        \resumeItem{Wrote native \textbf{Swift} code for iOS widgets alongside \textbf{Dart} and \textbf{JavaScript}; designed efficient data models and caching to reduce Firestore reads/writes by \textbf{30\%} and integrated Firebase FCM tokens for push notifications.}
        \resumeItem{Built and debugged web service (HTTPS callable functions), utilized GCP logging/metrics to fix reliability issues.}
        \resumeItem{Led a team in Northwestern's startup incubator (The Garage); shipped features using Git version control.}
      \resumeItemListEnd

    \resumeSubheading
      {Clemson University}{\daterange{Jun 2025}{Sep 2025}}
      {Research Assistant}{Clemson, SC}
      \vspace{2pt}
      \resumeItemListStart
        \resumeItem{Developed a serverless web app with \textbf{React/Node.js} for user check-in for lab machinery. Used \textbf{AWS RDS} to track user sessions and machine usage across shared equipment \& \textbf{S3} to store lab setting snapshots \& survey data}
        \resumeItem{Implemented a \textbf{CI/CD} pipeline using GitHub Actions to automatically build, test, and deploy after every commit}
        \resumeItem{Built and deployed a Hugo static website used by \textbf{200+} internal users to access documentation and lab resources.}
        \resumeItem{Debugged cross platform runtime issues in a \textbf{Linux Docker} container, identifying several OS-dependent bugs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Research}
  \resumeSubHeadingListStart
   \resumeProjectHeading
      {\textbf{Prescience Lab (Prof. Peter Dinda)} \textbar\ \emph{C/C++, RDMA, InfiniBand}}{\daterange{Dec 2025}{Present}}
      \vspace{2pt}
      \resumeItemListStart
        \resumeItem{Designed an RDMA gather collective in \textbf{C/C++} over \textbf{libibverbs}, translating a tree-based MPI gather into a triggered architecture that offloads the gather to the NIC and removes the CPU from the critical path.}
        \resumeItem{Reduced per-node operations from a 3-step (RDMA write, atomic fetch-and-add, doorbell write) sequence by exploiting InfiniBand within-QP ordering guarantees to eliminate explicit memory fences.}
        \resumeItem{Engineered a \textbf{kernel-bypass} networking flow for direct NIC-to-memory communication across supercomputing-cluster nodes, using MPI as an out-of-band bootstrap channel.}
      \resumeItemListEnd
  

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart



    \resumeProjectHeading
      {\textbf{Reliable Transport Protocol from Scratch} \textbar\ \emph{Python, Concurrency, Networking}}{\daterange{Dec 2025}{March 2026}}
      \vspace{2pt}
      \resumeItemListStart
        \resumeItem{Engineered a copy of TCP, simulating packet loss, data corruption, and ensuring reliable delivery through sequence numbering, MD5 packet hashing, and timeout based packet retransmission.}
        \resumeItem{Maximized network throughput by implementing pipelined ACKs and background listener threads.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Test Driven Monopoly Game} \textbar\ \emph{Java, JUnit 5, EasyMock, GitHub Actions}}{March 2026 - Jun 2026}
      \vspace{2pt}
      \resumeItemListStart
        \resumeItem{Built a full Java Monopoly engine with a team using \textbf{TDD} and \textbf{BVA}; achieved \textbf{100\%} branch/line coverage (JaCoCo) with mutation testing (PITest) and automated CI/CD regression on every commit.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages}{: C/C++, Python, Java, Rust, JavaScript/TypeScript, SQL (Postgres), Swift, Go} \\
   \textbf{Frameworks \& Stack}{: React, Express, Flutter, Flask, PyTorch, TensorFlow, AWS, Kubernetes, Firebase, Docker} \\
   \textbf{Systems \& Tools}{: Linux, Git, CI/CD, RDMA/InfiniBand, libibverbs, Docker, Backend systems/APIs}
  }}
\end{itemize}

\end{document}